\documentclass[9pt]{developercv} % Default font size, values from 8-12pt are recommended

\usepackage{graphics, subfigure}
% \usepackage[none]{hyphenat}

\begin{document}

\begin{minipage}[t]{0.4\textwidth} % 45% of the page width for name
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% If your name is very short, use just one of the lines below
	% If your name is very long, reduce the font size or make the minipage wider and reduce the others proportionately
	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Jack}}}}} % First name
	
	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Malcom}}}}} % Last name
	
	\vspace{6pt}
	
	{\huge Freshman Developer} % Career or current job title
\end{minipage}
\begin{minipage}[t]{0.3\textwidth} % 27.5% of the page width for the first row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	% Other icons can be found by referring to fontawesome.pdf (supplied with the template) and using the word after \fa in the command for the icon you want
	\icon{MapMarker}{12}{Fayetteville Arkansas}\\
	\icon{Phone}{12}{+1 815 570 7086}\\
	\icon{At}{12}{\href{mailto:jackxmalcom@gmail.com}{jackxmalcom@gmail.com}}\\	
\end{minipage}
\begin{minipage}[t]{0.3\textwidth} % 27.5% of the page width for the second row of icons
	\vspace{-\baselineskip}
	\icon{Globe}{12}{\href{https://jackmal.com}{jackmal.com (Work in progress)}}\\
	\icon{Github}{12}{\href{https://github.com/dizeeee}{github.com/dizeeee}}\\
\end{minipage}

\vspace{0.5cm}

	\begin{minipage}[t]{0.45\textwidth}
		\vspace{-\baselineskip} % Required for vertically aligning minipages
		\cvsect{About me}

		I am a nineteen year old freshman currently majoring in Computer Science at the University of Arkansas. I have a background in simple server management and web design.

	\end{minipage}
	\hfill % Whitespace between
	\begin{minipage}[t]{0.5\textwidth} % 50% of the page for the skills bar chart
		\vspace{-\baselineskip} % Required for vertically aligning minipages
		\cvsect{Skills}
		\skill{ubuntu}
		\skill{nodejs}
		\skill{java}
		\skill{html}
		\skill{css}
		\skill{javascript}
		\vspace{.2cm}\\
		\skill{cpp}
		\skill{git}
		
	\end{minipage}

\vspace{0.5cm}


\cvsect{Education}

\begin{entrylist}
	\entry
		{2018 - Current}
		{Computer Science BS}
		{}
		{University of Arkansas, Fayetteville, Arkansas}
	\entry
		{2014 -- 2018}
		{High School}
		{}
		{Lincoln-Way East, Frankfort, Illinois}
\end{entrylist}

\cvsect{Experience}

\begin{entrylist}
	\entry
		{Mar. 2019}
		{4th place in Hackathon}
		{ACM Spring Hackathon (Sponsored by J.B. Hunt)}
		{My team placed 4th out of 19 at the Spring 2019 Hackathon. We used serial output from arduinos to update a web server with showing loads of various trucks in real time. The team was comprised mostly of freshman, and the source code can be found on my github in the spinghackathon2019 repo.\
		\newline\texttt{Node.js}\slashsep\texttt{C}\slashsep\texttt{HTML}\slashsep\texttt{CSS}}
\end{entrylist}

\begin{entrylist}
	\entry
		{2016 - Current}
		{Library Shelver}
		{Frankfort Public Library}
		{As one of the oldest library shelvers, I am responsible for training new hires. I have trained all of the shelvers currently working in the library today.}\
\end{entrylist}

\cvsect{Awards}

\begin{entrylist}
	\entry
		{Jan. 2018}
		{Eagle Scout with three palms}
		{Frankfort Troop 270}
		{I am an Eagle Scout and have been active in the program since first grade. My Eagle Project was to build a Gaga Ball pit for our local park district. This involved weeks of planning, fundraising, and prep work to complete. The contstruction itself took three days and I led about 20 other Scouts in total during the process.}
\end{entrylist}

\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages

	\cvsect{Languages}
	
	\textbf{English} - Native\\
	\textbf{German} - Intermediate (3 Years)\\
\end{minipage}
\hfill
\begin{minipage}[t]{0.25\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	\cvsect{Clubs}
	
	\textbf{ACM} - 2 Semesters\\
	\textbf{Game Club} - 2 Semesters\\
\end{minipage}
\hfill
\begin{minipage}[t]{0.4\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	\cvsect{Source}
	
	This entire resume is written using LaTeX and is completely open source. All source code is hosted on my Github in the \href{https://www.github.com/Dizeeee/resume}{resume repo.}
\end{minipage}

%----------------------------------------------------------------------------------------

\end{document}
